---
title: "Introducing the ser R package"
subtitle: "Projects, code, and contributing"
output:
  xaringan::moon_reader:
    css: ["default", "theme.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, tibble.max_extra_cols = 6, tibble.width = 60)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.align = "center", dpi = 320)
library(rtweet)
```

class: inverse, center, middle

# **Find the package here:**
## https://github.com/SERTwitter/ser

---

class: inverse

# *Active Projects*

1. Weekday autotweeting
2. Daily email summary
3. Pre-meeting tweets

---

class: inverse

# *Helper tools*

1. Emailing on error
2. `ser_token()`
3. `source_ser()`

---



class: inverse

## *2019-2020 Projects*

1. Tweeting junior researcher papers
2. Calendar event tweets
3. Improving email summaries
4. Tweet Dashboard
4. Maintenance
5. Server deployment

---

class: inverse, center, middle

# **Let's take a look at ser**

---

class: inverse, center, middle

# **How to contribute**

---

## Submit a **pull request**

```{r, eval = FALSE}
library(usethis)
# download and open the package
create_from_github("SERTwitter/ser")
```

--

```{r, eval = FALSE}
# Create a new branch and set up PR
pr_init("branch_name")
# [Work on your code]
```

--

```{r, eval = FALSE}
# Send your code to GitHub
pr_push()
```

--

```{r, eval = FALSE}
# Get any changes from GitHub
pr_pull()
```

--

```{r, eval = FALSE}
# Clean up
pr_finish()
```

---

class: inverse, center, middle

# **Example: updating the README**

---

class: inverse

# *Workflow*

1. Create your script (`use_ser_script()`)
2. Submit a pull request (`pr_*()`)
3. Malcolm reviews 
4. Malcolm deploys (`source_ser()`)

--

### **I'll help you on any part of these!**

---

class: inverse, center, middle

# **There's a few things you'll need to know the basics about**

---

class: inverse, center, middle

# **R Packages**
## [R Packages: The Book!](http://r-pkgs.had.co.nz/)


---

class: inverse, center, middle

# **git and GitHub**
## [Happy git with R](http://happygitwithr.com)
## [usethis PR Helpers vignette](https://usethis.r-lib.org/articles/articles/pr-functions.html)

---

class: inverse

## *2019-2020 Projects*

1. Tweeting junior researcher papers
2. Calendar event tweets
3. Improving email summaries
4. Tweet Dashboard
4. Maintenance
5. Server deployment

