---
title: "Accessing Twitter Data"
subtitle: "with rtweet"
output:
  xaringan::moon_reader:
    css: ["default", "theme.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, tibble.max_extra_cols = 6, tibble.width = 60)
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.align = "center", dpi = 320)
library(rtweet)
```

class: inverse, center

# Getting started
## *Log in* to the SER Twitter account

## Install rtweet (if needed) and load

```{r, eval=FALSE}
install.packages("rtweet")
library(rtweet)
```

---

# Authenticate via browser
## https://developer.twitter.com/en/apps

```{r, eval=FALSE}
token <- create_token(
  app = "tweet_tokens_ser",
  consumer_key = "[CONSUMER KEY]",
  consumer_secret = "[SECRET CONSUMER KEY]",
  acess_token = "[SECRET ACCESS KEY]",
  access_secret =  "[SECRET ACCESS KEY]"
)
```

---

# Use `ser_token()` instead

--

```{r, eval = FALSE}
library(ser)
# add tokens with usethis::edit_r_environ()
ser_token()
```

--

```{r, echo=FALSE}
library(ser)
# add tokens with usethis::edit_r_environ()
ser_token()
```

---

# Get mentions

```{r twitter_mentions, cache = TRUE}
ser_mentions <- get_mentions(token = ser_token())
```

---

# Get mentions

```{r twitter_mentions2, echo = FALSE}
tibble::as_tibble(ser_mentions)
```

---

# Get mentions

```{r, eval=FALSE}
library(tidyverse)
ser_mentions %>% 
  ts_plot()
```

---

# Get mentions

```{r, echo=FALSE, fig.height=4}
library(tidyverse)
ser_mentions %>% 
  ts_plot()
```

---

# Most frequent mentioners

```{r}
mentioners <- lookup_tweets(
  ser_mentions$status_id, 
  token = ser_token()
)
```

---

# Most frequent mentioners

```{r, echo=FALSE}
mentioners
```

---

# Most frequent mentioners

```{r most_mentions_prep}
freq_mentioners <- mentioners %>% 
  count(screen_name) %>% 
  arrange(desc(n)) %>% 
  head(15) %>% 
  mutate(screen_name = paste0("@", screen_name))
```

---

# Most frequent mentioners

```{r, echo=FALSE}
freq_mentioners
```

---
# Most frequent mentioners

```{r most_mentions, eval=FALSE}
freq_mentioners %>% 
  ggplot(aes(fct_rev(fct_inorder(screen_name)), n)) +
    geom_col(col = "white", fill = "#0072B2") +
    coord_flip() +
    theme_minimal(base_size = 14) + 
    theme(panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank(),
          axis.title.y = element_blank()) +
    ylab("mentions")
```

---

```{r most_mentions_out, ref.label="most_mentions", echo=FALSE, fig.height=5}
```

---

# Get SER tweets

```{r twitter_timeline, cache = TRUE}
ser_tweets <- get_timeline(
  "societyforepi", 
  n = 1e5, 
  token = ser_token()
)
```

---

# Get SER tweets

```{r twitter_timeline2, echo=FALSE}
ser_tweets
```

---

# Get SER tweets

```{r, eval = FALSE}
ser_tweets %>% 
  ts_plot()
```

---

# Get SER tweets

```{r, echo = FALSE, fig.height=4}
ser_tweets %>% 
  ts_plot()
```

---

# Most liked tweets

```{r most_liked_tweets, eval=FALSE}
library(ggrepel)
ser_tweets %>% 
  arrange(desc(favorite_count)) %>% 
  head(100) %>% 
  mutate(id = 1:n(), label = ifelse(id %in% c(1:3, 6, 10), str_wrap(text), "")) %>% 
  arrange(favorite_count) %>%
  ggplot(aes(fct_inorder(status_id), favorite_count)) +
    geom_jitter(col = "white", fill = "#0072B2", shape = 21, size = 2.5) +
    geom_label_repel(aes(label = label), size = 2.5, force = 4, nudge_y = 3, point.padding = .5) +
    theme_minimal(base_size = 14) +
    theme(axis.text.x = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank()) +
    scale_y_continuous(breaks = seq(0, 150, 25)) +
    labs(x = "tweet", y = "favorites")
```

---

```{r most_liked_tweets_out, ref.label="most_liked_tweets", echo=FALSE, fig.height=5}
```

---

# Most retweeted tweets

```{r most_rt_tweets, eval=FALSE}
library(ggrepel)
ser_tweets %>% 
  arrange(desc(retweet_count)) %>% 
  filter(!is_retweet) %>% 
  head(100) %>% 
  mutate(id = 1:n(), label = ifelse(id %in% c(1:3, 6, 10), str_wrap(text), "")) %>% 
  arrange(retweet_count) %>%
  ggplot(aes(fct_inorder(status_id), retweet_count)) +
    geom_jitter(col = "white", fill = "#0072B2", shape = 21, size = 2.5) +
    geom_label_repel(aes(label = label), size = 2.5, force = 4, nudge_y = 3, point.padding = .5) +
    theme_minimal(base_size = 14) +
    theme(axis.text.x = element_blank(),
          panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank()) +
    scale_x_discrete(expand = expand_scale(add = 1)) +
    scale_y_continuous(breaks = seq(0, 150, 25)) +
    labs(x = "tweet", y = "retweets") 
```

---

```{r most_rt_tweets_out, ref.label="most_rt_tweets", echo=FALSE, fig.height=5}
```

---

# Post, follow, retweet, etc.

```{r, eval=FALSE}
post_tweet("this is to post a tweet", token = ser_token())

# retweet using status id
post_tweet(retweet_id = "1025872214472544256", token = ser_token())

# like using status id
post_favorite("1025872214472544256", token = ser_token())

# follow a user
post_follow("malco_barrett", token = ser_token())

# send a direct message
post_message(
  "you can even send a private message", 
  user = "malco_barrett", 
  token = ser_token()
)
```

---

class: inverse, center

# rtweet resources
## [Obtaining and using access tokens](https://rtweet.info/articles/auth.html)
## [Intro to rtweet: Collecting Twitter Data](https://rtweet.info/articles/intro.html)
## [Live streaming tweets](https://rtweet.info/articles/stream.html)

## [21 Recipes for Mining Twitter Data with rtweet](https://rud.is/books/21-recipes/)
